ODGI: scalable tools for pangenome graphs

### 2021-05-31 manuscript/main.tex
topic_2

    \topic{odgi viz, sort, drawn \& layout} pangenome visualization is important to gain insight
    into the relationship between the embedded genomes. \cmd{odgi viz} generates a 1D representation
    able to scale up to gigabase pangenome graphs (Figure~1\vphantom{\ref{fig:1}}).
    \cmd{odgi sort} finds the best node order to simplify the graph visualization by applying several
    cutting-edge sorting algorithms. \cmd{odgi drawn} extends the visualization in 2D,
    taking in input the layouts built by \cmd{odgi layout}.

>>>>

    \topic{odgi viz, sort, drawn \& layout} pangenome visualization
    provides convenient insight into genomic variation (see
    Fig.~\ref{fig:1}). \cmd{odgi viz} generates a linearized
    representation of the pangenome and is capable of handling full
    length human chromosomes (Fig.~\ref{fig:1}a).  \cmd{odgi sort}
    reorganises node order and simplifies the graph by applying
    several algorithms, including the novel `NAME the
    algorithm'. \cmd{odgi layout \& drawn} bring out the consensus
    graph (Fig.~\ref{fig:1}b).
